---
title: "Airport"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Austin-Bergstrom International Airport Analysis


```{r libraries}
#Bring in libraries needed for this problem
library(ggplot2)
library(tidyverse)
library(reshape2)
library(ggthemes)
#Read in the Airport data and drop NAs
airport <- read.csv("C:/Users/Shehz/Desktop/MSBA/Intro to Machine Learning/STA380-master/data/ABIA.csv")
attach(airport)
airport[is.na(airport)] <- 0
```
## Airport Analysis

First, we want to create a histogram with the arriving and departing flights at Austin-Bergstrom. This includes looking at flights that were not delayed. 

```{r flightHisto, echo = FALSE, warning= FALSE}
ggplot(data=airport)+geom_histogram(mapping=aes(x=ArrDelay),bins = 100,binwidth = 15,color = 'firebrick4', fill="tomato1") + 
  xlab("Arrival Delay") + ggtitle("Arrival Delay Count") +xlim(-50,450) + ylim(0,80000)+ylab("Count") +
  geom_vline(aes(xintercept  = mean(ArrDelay)), color = 'blue', linetype = 'dashed', size = 1) +theme_economist() +
  annotate(x=mean(ArrDelay),y=+Inf,label="Average Delay",vjust=1,geom="label") 

ggplot(data=airport)+geom_histogram(mapping=aes(x=DepDelay),bins = 100,binwidth = 15,color = 'slateblue', fill="skyblue1") + 
  xlab("Arrival Delay") + ggtitle("Departure Delay Count") +xlim(-50,450) +ylim(0,80000) +ylab("Count") +
  geom_vline(aes(xintercept  = mean(ArrDelay)), color = 'red', linetype = 'dashed', size = 1) + theme_economist() + 
  annotate(x=mean(DepDelay),y=+Inf,label="Average Delay",vjust=1,geom="label") 



paste0("The average arrival delay is ",round(mean(ArrDelay),2)," minutes.")
paste0("The average departure delay is ",round(mean(DepDelay),2)," minutes.")
```
As we can see from the arrival histogram, most flights coming into Austin-Bergstrom are on time/early or delayed by less than 10 minutes. The flight departure histogram shows there are more delays in departures than arrivals. The departing flights have a delay that is around 2 minutes longer than that of an arriving flight. 

## Carrier Analysis

Next, we want to analyze the performance of the carriers at Austin-Bergstrom Airport.


``` {r carrierCount, echo = FALSE, warning = FALSE}
ggplot(data=airport) + geom_histogram(mapping=aes(x=UniqueCarrier),stat="count", color = "darkorange4", fill = "tan2") + 
  ggtitle("Flights in-and-out of Austin by Carrier") + xlab("Carrier") + ylab("Number of Flights") + theme_economist() 

paste0("Southwest had the highest flight count at AIBA with ", sum(airport$UniqueCarrier == "WN"),".")
paste0("Followed by American Airlines who had an AIBA flight count of ", sum(airport$UniqueCarrier == "AA"),".")
paste0("The company with the least amount of flights at AIBA is Northwest Airlines with ",sum(airport$UniqueCarrier == "NW"), " flights.")
```

If I am an Austin resident looking to open an airline credit card, I would look closely at what Southwest offers since they have the most flights at AIBA.
Let's take a look at the portion of flights delayed by each carrier.

``` {r carrierNorm, echo = FALSE}
carr_arrdelay_count <- airport %>% group_by(UniqueCarrier) %>% summarise(carrier_arr_prob = length(ArrDelay[ArrDelay>0])/length(ArrDelay))
carr_depdelay_count <- airport %>% group_by(UniqueCarrier) %>% summarise(carrier_dep_prob = length(DepDelay[DepDelay>0])/length(DepDelay)) 

ggplot(data=carr_arrdelay_count) + geom_bar(mapping=aes(x=reorder(UniqueCarrier,carrier_arr_prob),y=carrier_arr_prob),stat="identity",position="dodge", color = 'firebrick4', fill = 'tomato1') +
  xlab("Carrier") + ylab("Portion Delayed") +ggtitle("Carrier")+ theme_economist() +
  ggtitle("Portion of Arriving Flights Delayed by Carrier")

ggplot(data=carr_depdelay_count) + geom_bar(mapping=aes(x=reorder(UniqueCarrier,carrier_dep_prob),y=carrier_dep_prob), stat="identity",position="dodge", color = 'slateblue', fill="skyblue1") +
  xlab("Carrier") + ylab("Portion Delayed") + ggtitle("Portion of Departing Flights Delayed by Carrier") +theme_economist()
```

Not all delays are created equal. We must know the average time(minutes) that a carrier will delay a flight before we can make a judgement about which airline we want to avoid on future trips.

``` {r carrierAvg, echo = FALSE}
carr_delay_df <- airport %>% group_by(UniqueCarrier) %>%  summarise(arr_delay_avg = mean(ArrDelay[ArrDelay>0]),dep_delay_avg = mean(DepDelay[ArrDelay>0]))
ggplot(data=carr_delay_df) + geom_bar(mapping=aes(x=reorder(UniqueCarrier,arr_delay_avg),y=arr_delay_avg),stat="identity",position="dodge", color = 'firebrick4', fill = 'tomato1') + xlab("Carrier") +
  ylab("Average Delay(minutes)") +ggtitle("Average Arrival Delay by Carrier")+ theme_economist()
  
ggplot(data=carr_delay_df) + geom_bar(mapping=aes(x=reorder(UniqueCarrier,dep_delay_avg),y=dep_delay_avg), stat="identity",position="dodge", color = 'slateblue', fill="skyblue1") + 
  xlab("Carrier") + ylab("Average Delay(minutes)") + ggtitle("Average Departure Delay by Carrier") +theme_economist()

#combine the plots to see how the arrival vs departure delays are per carrier to see if one carrier has more of one type
test_data_long <- melt(carr_delay_df,id="UniqueCarrier")
ggplot(data=test_data_long) + geom_bar(mapping=aes(x=UniqueCarrier,y=value,fill=variable), stat="identity",position="dodge") + ggtitle("Average Arrival and Departure Delay per Carrier")+xlab("Carrier") +
  ylab("Average Delay(minutes)") + scale_fill_discrete("Flight type", labels = c("Arrival","Delay")) + theme_economist()

```

ExpressJet Airlines and Southwest Airlines have the highest portion of departing flights delayed, but ExpressJets' delays are around 10 minutes longer than Southwest delays. JetBlue is also intriguing because they are middle of the pack in terms of portion delayed, but their delays are avering over 30 minutes. US Airways has the shortest delays of any of the carriers(arrival and departure), but they have a pretty low flight count at Austin-Bergstrom, so chances are that we won't get many destination and time options to work with an airline like US Airways.

A 10 minute delay can be a little annoying, but a 25 minute delay can ruin your plans. We want to look into which carrier is most likely to have a 25 minute delay.

``` {r carrier25, echo = FALSE}
carr_prob_df <- airport %>% group_by(UniqueCarrier) 
carr_prob_df <- carr_prob_df %>% summarise(carr_delay_25 = length(CarrierDelay[CarrierDelay>25])/length(CarrierDelay))
test_data_long2 <- melt(carr_prob_df,id="UniqueCarrier")
ggplot(data=test_data_long2) + geom_bar(mapping=aes(x=reorder(UniqueCarrier,value),y=value),stat="identity",color ='darkgreen', fill = 'lightgreen') + ggtitle("Carrier Portion Delayed > 25 minutes") + ylab("Portion Delayed > 25 Minutes") + xlab("Carrier")
```

The portion of flights delayed more than 25 minutes is extremely low, but the airline with the highest portion delayed more than 25 minutes is Mesa Airlines. We don't believe that the portion of delays greater than 25 minutes is an important factor when planning a trip so we don't need to worry about a long delay messing up our itinerary. 

## Carrier Conclusion

Southwest and American Airlines have the most flights in-and-out of Austin-Bergstrom, therefore they will have the most time/route options of any carrier. Southwest is on the high-end of departure delays, but on the low-end in terms of arrival delays. If we had to choose between Southwest and American Airlines based on the data, we would choose American Airlines since they have a lower portion of departures getting delayed and their departure delays are shorter than Southwest. Leaving on time is more important to us than arriving on time. JetBlue and ExpressJet are airlines that we would avoid, but it won't be hard since they do not have many flight options at ABIA. 

## Calendar Analysis

First, lets examine at the number of flights per month at Austin-Bergstrom. 

``` {r monthCount, echo = FALSE}
ggplot(data=airport) + geom_histogram(mapping=aes(x=Month),stat="count",col =
                                        c("navyblue","navyblue","greenyellow","greenyellow","greenyellow","gold2","gold2","gold2","sienna2","sienna2","sienna2","navyblue"),
                                      fill = c("navyblue","navyblue","greenyellow","greenyellow","greenyellow","gold2","gold2","gold2","sienna2","sienna2","sienna2","navyblue")) + 
                                      ggtitle("Total Flights per Month in-and-out of Austin") +scale_x_continuous( breaks=c(0,1,2,3,4,5,6,7,8,9,10,11,12)) +ylab("Flight Count") +
                                      annotate(x=11,y=+Inf,label="Colored by Season",vjust=2,geom="label")
```

It is not surprising to see that the Spring and Summer have the highest flight count. We can not test this, but we believe Longhorn football is the reason for less flights in the Fall. 

Texas weather can be hard to predict and changes so quickly, but we wanted to know which months have the most weather delays in Austin, Texas. 

``` {r weatherAnalysis,echo = FALSE}
weath_delay_df <- airport %>% group_by(Month) 
weath_delay_df <- weath_delay_df %>% summarise(weath_delay_count = length(WeatherDelay[WeatherDelay>0])) 
test_data_long3 <- melt(weath_delay_df,id="Month")
ggplot(data=test_data_long3) + geom_bar(mapping=aes(x=Month,y=value),stat="identity",col =
                                          c("navyblue","navyblue","olivedrab4","olivedrab4","olivedrab4","gold2","gold2","gold2","sienna2","sienna2","sienna2","navyblue"),fill =
                                          c("navyblue","navyblue","olivedrab4","olivedrab4","olivedrab4","gold2","gold2","gold2","sienna2","sienna2","sienna2","navyblue")) +
  scale_x_continuous(breaks=c(0,1,2,3,4,5,6,7,8,9,10,11,12)) + ggtitle("Weather Delays per Month") + ylab("Weather Delay Count") + annotate(x=11,y=+Inf,
                                            label="Colored by Season",vjust=2,geom="label") + theme_economist()
```
March has the most amount of weather delays, followed by December and August. When looking at seasonality the Winter months have the most of weather delays, while Autum has the least amount. 

Lastly, we want to investigate which months have the most delays and which months have the highest portion of delayed flights. 

```{r monthDelayCount, echo = FALSE}
month_deparr_df <- airport %>% group_by(Month) 
month_deparr_df <- month_deparr_df %>% summarise(month_arr = length(ArrDelay[ArrDelay>0]),
                                                 month_dep = length(DepDelay[DepDelay>0])) 
test_data_long4 <- melt(month_deparr_df,id="Month")

ggplot(data=month_deparr_df) + geom_bar(mapping=aes(x=Month,y=month_arr), stat="identity",position="dodge", color = 'firebrick4', fill = 'tomato1') + xlab("Month") + ylab("Delay Count") +
  ggtitle("Arrival Delay Count by Month")+ theme_economist() + scale_x_continuous( breaks=c(0,1,2,3,4,5,6,7,8,9,10,11,12))

ggplot(data=month_deparr_df) + geom_bar(mapping=aes(x=Month,y=month_dep), stat="identity",position="dodge", color = 'slateblue', fill="skyblue1") +  xlab("Month") + ylab("Delay Count") +
  ggtitle("Departure Delays by Month") +theme_economist() + scale_x_continuous( breaks=c(0,1,2,3,4,5,6,7,8,9,10,11,12))

ggplot(data=test_data_long4) + geom_bar(mapping=aes(x=Month,y=value,fill=variable),stat="identity",position="dodge") + scale_x_continuous( breaks=c(0,1,2,3,4,5,6,7,8,9,10,11,12)) +
  ggtitle("Arrival and Departure Delays per Month") + ylab("Delay Count") + scale_fill_discrete("Flight type", labels = c("Arrival","Delay"))
```

March and June have the most delays, and that is not shocking since Spring Break and early Summer are huge travel times at Austin-Bergstrom. We are surprised at the amount of delays in December since that is a month with the second lowest flight count in-and-out of Austin, Texas. 

Do a higher portion of flights get delayed in December? We want to test that question next. 

``` {r monthDelayNorm, echo = FALSE}
month_delay_prob_df <- airport %>% group_by(Month)
month_delay_prob_df <- month_delay_prob_df %>% summarise(month_arr_prob = length(ArrDelay[ArrDelay>0])/length(ArrDelay),
                                                          month_dep_prob = length(DepDelay[DepDelay>0])/length(DepDelay))
test_data_long5 <- melt(month_delay_prob_df,id="Month")

ggplot(data=month_delay_prob_df) + geom_bar(mapping=aes(x=Month,y=month_arr_prob), stat="identity",position="dodge", color = 'firebrick4', fill = 'tomato1') + xlab("Month") +
  ylab("Portion Delayed") +ggtitle("Arrival Delay Portion per Month")+ theme_economist() +scale_x_continuous( breaks=c(0,1,2,3,4,5,6,7,8,9,10,11,12))

ggplot(data=month_delay_prob_df) + geom_bar(mapping=aes(x=Month,y=month_dep_prob), stat="identity",position="dodge", color = 'slateblue', fill="skyblue1") + xlab("Month") +
  ylab("Portion Delayed") + ggtitle("Departure Delay Portion per Month") +theme_economist() +scale_x_continuous( breaks=c(0,1,2,3,4,5,6,7,8,9,10,11,12))


ggplot(data=test_data_long5) + geom_bar(mapping=aes(x=Month,y=value,fill=variable),stat="identity",position="dodge") +scale_x_continuous( breaks=c(0,1,2,3,4,5,6,7,8,9,10,11,12)) +
  ggtitle("Portion of Flights Being Delayed per Month") + ylab("Portion Delayed") + scale_fill_discrete("Flight type", labels = c("Arrival","Delay"))
```
If you decide to fly out of Austin-Bergstrom in December, you have around a 50% chance of having your flight delayed. This graph adds validity to notion that airports around the holidays get crazy. They even made a movie about it called "Planes, Trains, and Automobiles".

## Calendar Conclusion

The Spring and Summer are the busiest seasons at ABIA. March(spring break) and June(school is finished) have the highest amount of delays, while December has the highest portion of delays. March is the month with the most amount of weather delays, but the Winter is the season with the most weather delays. In the future, we would like to revisit this dataset with more years so we can identify is March is typically a bad weather month in Austin or was March 2008 a bad weather month in Austin. The information we learned in the calendar section confirmed priors we had from our traveling experience, but it is nice to get confirmation. 

## Destination Analysis

We are interested to know where Austin residents are flying and how many of the popular destinations have a high portion of delayed flights.

``` {r destFlightCount, echo = FALSE}
dest_count <- airport %>% group_by(Dest) %>% filter(Dest != "AUS") %>% summarise(DestCount = n()) %>% arrange(desc(DestCount)) %>% slice(0:15)
test_data_long7 <- melt(dest_count, id = "Dest")
dest_delay <- airport %>% group_by(Dest) %>% filter(Dest != "AUS") %>% summarise(DestDelayProb = length(DepDelay[DepDelay>0])/length(DepDelay)) %>% arrange(desc(DestDelayProb))  %>% slice(0:15)
test_data_long6 <- melt(dest_delay,id="Dest")


ggplot(data=test_data_long7) + geom_bar(mapping=aes(x=reorder(Dest,value),y=value),
                                            stat="identity",position="dodge", color = 'firebrick4', fill = 'tomato1') + xlab("Destination") + 
  ylab("Flight Count to Destination") +ggtitle("Top 15 Destinations from ABIA")+ theme_economist()

ggplot(data=test_data_long6) + geom_bar(mapping=aes(x=reorder(Dest,value),y=value),
                                            stat="identity",position="dodge", color = 'slateblue', fill="skyblue1") + 
  xlab("Destination") + ylab("Portion Delayed") + ggtitle("Top 15 Portion of Departing Flights Delayed by Destination") +theme_economist()
```
We have a large amount of flights that are in the state of Texas with 4 of the top 7 airport destinations being in Texas. When we look at the portion of flights delayed by destination, Houston(Hobby) and Newark are the only airports in the top 15 flight count and top 15 portion delayed. There is only 1 flight to Des Moines, Iowa and it was delayed, so that explains why it has a high portion of flights delayed.

Nobody likes getting home later than expected, let's look at the arrival delays by flight origin location.

``` {r arrFlightCount, echo = FALSE}
arr_count <- airport %>% group_by(Origin) %>% filter(Origin != "AUS") %>% summarise(ArrCount = n()) %>% arrange(desc(ArrCount)) %>% slice(0:15)
test_data_long8 <- melt(arr_count, id = 'Origin')
arr_delay <- airport %>% group_by(Origin) %>% filter(Origin != "AUS") %>% summarise(ArrDelayProb = length(ArrDelay[ArrDelay>0])/length(ArrDelay)) %>% arrange(desc(ArrDelayProb)) %>% slice(0:15)
test_data_long9 <- melt(arr_delay,id="Origin")


ggplot(data=test_data_long8) + geom_bar(mapping=aes(x=reorder(Origin,value),y=value),
                                        stat="identity",position="dodge", color = 'firebrick4', fill = 'tomato1') + xlab("Flight Origin Location") + 
  ylab("Flight Count") +ggtitle("Top 15 Airports flying into Austin")+ theme_economist()

ggplot(data=test_data_long9) + geom_bar(mapping=aes(x=reorder(Origin,value),y=value),
                                        stat="identity",position="dodge", color = 'slateblue', fill="skyblue1") + 
  xlab("Flight Origin Location") + ylab("Portion Delayed") + ggtitle("Top 15 Portion of Arriving Flights Delay by Origin") +theme_economist()
```

The arrival flight count looks pretty similar to the departure flight count. Newark is the only airport on both lists again! They need to get it together. 

## Destination Analysis

A large chunk of flights leaving Austin-Bergstrom end up staying in the state of Texas. Most of the popular flight routes are pretty efficient and do not have a large portion of flights being delayed(arrival and departure). You just might want to think twice before you book a flight to Newark, New Jersey. 


