---
title: "R_HW_6_Association Rule Mining"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Problem
type the problem here
```{r}
library(tidyverse)
library(arules)
library(arulesViz)
library(ggplot2)

raw = read.delim("groceries.txt",header= FALSE)
df = data.frame(user=character(), 
                items=character(), 
                stringsAsFactors=FALSE) 

for (i in 1:nrow(raw)){
  string = raw[i,]
  basket = unlist(strsplit(string, ","))
  user.id = rep(i, length(basket))
  df = rbind(df, data.frame(user = user.id,items = basket))
}

str(df)
summary(df)

#ordering the plots
items_count = aggregate(df$items,by = list(df$items),FUN =length)
colnames(items_count) <- c("item", "total") 
items_count = items_count[order(items_count$total,decreasing = TRUE),]  #sort
items_count$item <- factor(items_count$item, levels = items_count$item)  # to retain the order in plot.
head(items_count, 4)

theme_set(theme_bw())
```
## Exploratory Analysis
```{r}
# Draw plot
ggplot(items_count[1:20,], aes(x=item, y=total)) + 
  geom_bar(stat="identity", width=.5, fill="tomato") + 
  labs(title="Top 10 Popular Groceries") + 
  theme(axis.text.x = element_text(angle=90,vjust = 0))
```
Whole Milk was by far the most popular grocery with a count near 2500.
```{r}
df$user = factor(df$user)
groceries = split(x=df$items, f=df$user)
groceries = lapply(groceries, unique)

grotrans = as(groceries, "transactions")
summary(grotrans)
```
```{r}
groc_rules = apriori(grotrans,parameter=list(support=.005, confidence=.1, maxlen=5))
plot(groc_rules)
```
```{r}
plot(groc_rules, method='two-key plot')
```

From this scatter plot, we can see that the large majority of rules have support values less than 0.025 but a varying confidence. There also is a slight correlation that the larger lifts have lower confidences. We can see that the size of the rules are clustred in a way that lower support valued rules have larger rule sizes.

##Networks
```{r}
groc_rule_1 = apriori(groceries,parameter=list(support=.05, confidence=.1, minlen=2))
inspect(groc_rule_1)
#6 rules bc high support and confidence
inspect(subset(groc_rule_1, subset=lift > 3))
inspect(subset(groc_rule_1, subset=confidence > 0.5))
inspect(subset(groc_rule_1, subset=lift > 3 & confidence > 0.5))
plot(groc_rule_1,method="graph")
```

```{r}
groc_rule_2 = apriori(groceries,parameter=list(support=.03, confidence=.05, minlen=2))
inspect(groc_rule_2)
#38 rules
inspect(subset(groc_rule_2, subset=lift > 3))
inspect(subset(groc_rule_2, subset=confidence > 0.5))
inspect(subset(groc_rule_2, subset=lift > 3 & confidence > 0.5))
plot(groc_rule_2,method="graph")
```

```{r}
groc_rule_3 = apriori(groceries,parameter=list(support=.01, confidence=.01, minlen=2))
inspect(groc_rule_3)
#125 rules
inspect(subset(groc_rule_3, subset=lift > 3))
inspect(subset(groc_rule_3, subset=confidence > 0.5))
inspect(subset(groc_rule_3, subset=lift > 3 & confidence > 0.5))
plot(groc_rule_3,method="graph")
```

From these, we can see that whole milk is the most important item, and that makes sense as that is a staple in most diets. Next would be yogurt and other vegetables, which also makes sense as they are staple items. Some other things that we see, are that meat is correlated with vegetables, so putting some coupons or such for meat in the veggie section could help sell meat. Can put some berries next to yogurt to encourage people to buy berries and make a nice parfait.
