---
title: "R_HW_6_Association Rule Mining"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages('tidyverse')
#install.packages('arules')  
#install.packages('arulesViz')
```

```{r}
library(tidyverse)
library(arules)  # has a big ecosystem of packages built around it
library(arulesViz)
```

#some data processing
```{r, include=False}
raw = read.delim("groceries.txt",header= FALSE)
df = data.frame(user=character(), 
                 items=character(), 
                 stringsAsFactors=FALSE) 

for (i in 1:nrow(raw)){
  string = raw[i,]
  basket = unlist(strsplit(string, ","))
  user.id = rep(i, length(basket))
  df = rbind(df, data.frame(user = user.id,items = basket))
}

# Turn user into a factor
df$user = factor(df$user)

# apriori algorithm expects a list of baskets in a special format
# In this case, one "basket" of songs per user
# First split data into a list of artists for each user
grocery = split(x=df$items, f=df$user)

## Remove duplicates ("de-dupe")
grocery = lapply(grocery, unique)
```

# Most frequent items include:
whole milk, other vegetables, rolls/bun, soda, yogurt

```{r}
itemtrans = as(grocery, "transactions")
summary(itemtrans)
```

# Most frequent items include:
whole milk, other vegetables, rolls/bun, soda, yogurt
```{r}
#calculates support for frequent items
frequentItems <- eclat (itemtrans, parameter=list(supp=0.06, maxlen=10)) 
inspect(frequentItems)
#plot frequent items
itemFrequencyPlot(itemtrans, topN=10, type="absolute", main="Item Frequency") 
```

```{r}
# Now run the 'apriori' algorithm
# Look at rules with support > .005 & confidence >.1 & length (# items) <= 5
itemrules = apriori(itemtrans,parameter=list(support=.005, confidence=.1, maxlen=5))
inspect(itemrules)
```

# high lift rules tend to have low support

```{r}
# plot all the rules in (support, confidence) space
plot(itemrules)
```

```{r}
# plot all the rules in (support, lift) space
plot(itemrules, measure = c("support", "lift"), shading = "confidence")
```

```{r}
# "two key" plot: coloring is by size (order) of item set
plot(itemrules, method='two-key plot')
```

# Sorted by 'high-confidence'
top 10 are highly concentrated on whole milk.

```{r}
rules_conf <- sort(itemrules, by="confidence", decreasing=TRUE) # 'high-confidence' rules.
inspect(rules_conf[1:10])
```
```{r}
inspect(subset(rules_conf, confidence>0.6)) # show the support, lift and confidence for all rules
```
# Sorted by 'high-lift'
top 10 are evenly distributed.

```{r}
rules_conf <- sort(itemrules, by="lift", decreasing=TRUE) # 'high-confidence' rules.
inspect(rules_conf[1:10])
```

# To find what factors influenced purchase of whole milk

```{r}
itemrules2 <- apriori(data=itemtrans, parameter=list(supp=0.005,conf=0.1), appearance=list (default="lhs",rhs="whole milk"), control = list (verbose=F)) # get rules that lead to buying 'whole milk'
rules_conf2 <- sort(itemrules2, by="confidence", decreasing=TRUE) # 'high-confidence' rules.
inspect(head(rules_conf2))
```

# To find out what products were purchased after/along with whole milk

```{r}
itemrules3 <- apriori (data=itemtrans, parameter=list(supp=0.005,conf=0.1,minlen=2), appearance= list(default="rhs",lhs="whole milk"), control = list (verbose=F)) # those who bought 'milk' also bought..
rules_conf3 <- sort(itemrules3, by="confidence", decreasing=TRUE) # 'high-confidence' rules.
inspect(head(rules_conf3))
```

```{r}
# graph-based visualization
sub1 = subset(itemrules, subset=confidence>0.5 & support>0.005)
summary(sub1)
plot(sub1, method='graph')

plot(head(sub1,50,by='lift'), method='graph')
```

```{r}
library(tidyverse)
library(arules)
library(arulesViz)
library(ggplot2)

raw = read.delim("groceries.txt",header= FALSE)
df = data.frame(user=character(), 
                items=character(), 
                stringsAsFactors=FALSE) 

for (i in 1:nrow(raw)){
  string = raw[i,]
  basket = unlist(strsplit(string, ","))
  user.id = rep(i, length(basket))
  df = rbind(df, data.frame(user = user.id,items = basket))
}

str(df)
summary(df)

#ordering the plots
items_count = aggregate(df$items,by = list(df$items),FUN =length)
colnames(items_count) <- c("item", "total") 
items_count = items_count[order(items_count$total,decreasing = TRUE),]  #sort
items_count$item <- factor(items_count$item, levels = items_count$item)  # to retain the order in plot.
head(items_count, 4)

theme_set(theme_bw())
```

```{r}
# Draw plot
ggplot(items_count[1:20,], aes(x=item, y=total)) + 
  geom_bar(stat="identity", width=.5, fill="tomato") + 
  labs(title="Top 10 Popular Groceries") + 
  theme(axis.text.x = element_text(angle=90,vjust = 0))
```

```{r}
df$user = factor(df$user)
groceries = split(x=df$items, f=df$user)
groceries = lapply(groceries, unique)

grotrans = as(groceries, "transactions")
summary(grotrans)
```

```{r}
groc_rule_1 = apriori(groceries,parameter=list(support=.05, confidence=.1, minlen=2))
inspect(groc_rule_1)
#6 rules bc high support and confidence
inspect(subset(groc_rule_1, subset=lift > 3))
inspect(subset(groc_rule_1, subset=confidence > 0.5))
inspect(subset(groc_rule_1, subset=lift > 3 & confidence > 0.5))
plot(groc_rule_1,method="graph")
```

```{r}
groc_rule_2 = apriori(groceries,parameter=list(support=.03, confidence=.05, minlen=2))
inspect(groc_rule_2)
#38 rules
inspect(subset(groc_rule_2, subset=lift > 3))
inspect(subset(groc_rule_2, subset=confidence > 0.5))
inspect(subset(groc_rule_2, subset=lift > 3 & confidence > 0.5))
plot(groc_rule_2,method="graph")
```

```{r}
groc_rule_3 = apriori(groceries,parameter=list(support=.01, confidence=.01, minlen=2))
inspect(groc_rule_3)
#125 rules
inspect(subset(groc_rule_3, subset=lift > 3))
inspect(subset(groc_rule_3, subset=confidence > 0.5))
inspect(subset(groc_rule_3, subset=lift > 3 & confidence > 0.5))
plot(groc_rule_3,method="graph")
```

From these, we can see that whole milk is the most important item, and that makes sense as that is a staple in most diets. Next would be yogurt and other vegetables, which also makes sense as they are staple items. Some other things that we see, are that meat is correlated with vegetables, so putting some coupons or such for meat in the veggie section could help sell meat. Can put some berries next to yogurt to encourage people to buy berries and make a nice parfait.
