---
title: "Exercise"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## green buildings
We found many flaws in the analysis done by the "excel guru". We disagree with his figures as he only took the median of rent from both non-green and green building, then use the differences between the two to calculate extra revenue. He did not consider other factors that might be affecting the relationship between rent and green status which make his calculation inefficient. Furthermore, he only took into account the initial cost of 100 mil and the 5% premium, without considering other cost-benefits such as savings on electrcity and gas usage in a green building. Next we will show some analysis we did to look for confounding variables.

```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggalt)
gb = read.csv("greenbuildings.csv")
gb$net = as.factor(gb$net)
gb$green_rating = as.factor(gb$green_rating)
gb$LEED = as.factor(gb$LEED)
gb$Energystar = as.factor(gb$Energystar)
gb$renovated = as.factor(gb$renovated)
gb$class_a = as.factor(gb$class_a)
avg_age = median(gb[gb$green_rating == 1,]$age)
```

Here, we are doing some data exploratory analysis on the dataset to discover trends and correlations.
```{r}
theme_set(theme_classic())

g1 <- ggplot(gb, aes(Rent)) + scale_fill_brewer(palette = "Spectral") +                geom_histogram(aes(fill=stories),binwidth = 2, 
                   col="black", 
                   size=.1)

g1 + facet_wrap( ~ green_rating) + 
    labs(title="Distribution of rent across all buildings", y="Number of buildings", x="Rent")

# Zoom in without deleting the points outside the limits.
g1 + facet_wrap( ~ green_rating) + coord_cartesian(xlim=c(0,100)) +
    labs(title="Distribution of rent across all buildings", subtitle="Rent below $100",
    y="Number of buildings", x="Rent")

# Zoom in to take a look at the extreme case.
g1 + facet_wrap( ~ green_rating) + coord_cartesian(xlim=c(100,300),ylim=c(0,25)) +
  labs(title="Distribution of rent across all buildings", subtitle="Rent above $100",
    y="Number of buildings", x="Rent")

g2 <- ggplot(gb, aes(leasing_rate)) + scale_fill_brewer(palette = "Spectral") +                geom_density(aes(fill=factor(green_rating)), alpha=0.8)
g2 + facet_wrap( ~ green_rating) + 
    labs(title="Distribution of leasing rate across all buildings", y="Density", x="Leasing Rate")


# There are many factors that can have an effect on rent, like location, building quality, appliances and Other amenities, tenant/use mix, etc. Now we know that the target project is a new 15-story mixed-use building on East Cesar Chavez, just across I-35 from downtown. Since we have story information in the dataset, let's focus on the situation of 15-story buildings.

# From the graphic, we can conclude that among 15-story building:
# 1.the average rent of green buildings is higher than that of non-green buildings;
# 2.the average occupancy rate of green buildings is higher than that of non-green buildings;
# 3.all green buildings have a class of a or b (however, does this bring extra cost)?


story15 = dplyr::filter(gb,stories==15)
story15.class = story15 %>% filter(class_a == 0 & class_b == 0)

theme_set(theme_bw())
g3 <- ggplot(story15, aes(leasing_rate,Rent))
g3 + geom_point(aes(col=green_rating, size=age)) + 
     geom_encircle(aes(x=leasing_rate, y=Rent), 
                data=story15.class, 
                color="red", 
                size=2, 
                expand=0.08)
```

Here, we analyzed some variables that might be affecting the relationship between green status and rent.
```{r}
#From this plot we can see that a majority of the green buildings are of class a
classa_b = ggplot(data=gb) + geom_bar(mapping = aes(x=class_a, fill = green_rating),stat="count",position = "dodge")

classa_b

#Then we dived in on the relationship between class a and rent specifically and saw that class a building generally have a higher rent
all_class = ggplot(data=gb) + geom_boxplot(mapping = aes(x=class_a,y=Rent,color = green_rating))

all_class + coord_cartesian(ylim=c(0,100))

#Since most green buildings are of class a, class a can be a confounding variable that is also a part of the reason why rent increases in respect to green status. To adjust that, we can hold the class variable constant across buildings, and compute median rent from those buildings. 

```

Profit calculations with class_a eqauls to 1.
```{r}
#Create database that has only green buildings and one that has no green buildings
greenOnly = gb %>% filter(green_rating == 1 & class_a == 1)
nonGreen = gb %>% filter(green_rating == 0 & class_a == 1)

#Calculate count, median rent, median leasing rate for green buildings
greenCount <- greenOnly %>% summarise(n())
medGreenCapacity <- greenOnly %>% summarise(median(leasing_rate)/100)
medGreenRent <- greenOnly %>%   summarise(median(Rent))


#Calculate count, median rent, median leasing rate for non-green buildings
nonGreenCount <- nonGreen %>% summarise(n())
medNonGreenCapacity <- nonGreen %>% summarise(median(leasing_rate)/100)
medNonGreenRent <- nonGreen %>% summarise(median(Rent))

#Calculate median gas and electric cost 
medGasCost <- gb %>% summarise(median(Gas_Costs))
medElectricCost <- gb %>% summarise(median(Electricity_Costs))

#setSquareFootage for further calculations
sqFt = 250000
#Set a weight of .9 for green electric and gas cost since they use less than non-green buildings. 
#This is a subjective number and can be changed with future research regarding how much will actually be saved
greenCostWeighted = .9

#Calculate expected rent, expense, and profit if our building was green
#Weight rent by expected capacity and calculate rent by adding rent diff b/w green/non green buildings
#and adding that to the median non green rent. 
greenExpectedRent <- medGreenRent * medGreenCapacity * sqFt
#Weight expenses by expected savings by using less resources
greenExpectedExpense <- (sqFt * medGasCost * greenCostWeighted) + (sqFt * medElectricCost * greenCostWeighted)
greenExpectedProfit <- greenExpectedRent - greenExpectedExpense

#Calculate expected rent, expense, and profit if our building was not green. 
#Weight rent by expected capacity and calculate rent by multiplying square feet by median rent of non green
#buildings. Expected expenses was not weighted because they will use all resources.

nonGreenExpectedRent <- medNonGreenRent * medNonGreenCapacity * sqFt
nonGreenExpectedExpense <- (sqFt * medGasCost) + (sqFt * medElectricCost)
nonGreenExpectedProfit <- nonGreenExpectedRent - nonGreenExpectedExpense

#Calculate the expected profit difference if the building chose to be green
buildingDiff <- greenExpectedProfit-nonGreenExpectedProfit


#Set green premium so we can calculate expected payback period and long-haul profits
options("scipen" = 100,"digits" = 4) #Gets rid of scientific notation
greenCert <- 100000000 *.05

paybackPeriod = greenCert/buildingDiff

print("Report")
paste0("Expected rent price for Green building: ",medGreenRent, " Expected rent price for Non-Green building:",medNonGreenRent )
paste0("Expected leasing rate for Green building: ",medGreenCapacity, " Expected rent price for Non-Green building:",medNonGreenCapacity )
paste0("Expected yearly rent for Green building: ",round(greenExpectedRent,2), " Expected yearly rent for Non-Green building:", round(nonGreenExpectedRent,2))
paste0("Expected electric Rate for the building: ",medElectricCost, " Expected gas Rate for the building: ",medGasCost )
paste0("Expected electric/gas usage for the Green building: ",greenCostWeighted, " Expected electric/gas usage for the Non-Green Building: 1" )
paste0("Expected expenses for the Green building: ",round(greenExpectedExpense,2), " Expected expenses for the Non-Green building: ",round(nonGreenExpectedExpense,2 ))
paste0("Expected profit for Green Building: ",round(greenExpectedProfit,2), " Expected profit for Non-Green Building: ",round(nonGreenExpectedProfit,2) )
paste0("Expected profit difference between a green and non-green building: ", round(buildingDiff,2))
paste0("Expected payback period: ", round(paybackPeriod,2))

```

Profit calculations with class_a eqauls to 0.
```{r}
#Create database that has only green buildings and one that has no green buildings
greenOnly = gb %>% filter(green_rating == 1 & class_a == 0)
nonGreen = gb %>% filter(green_rating == 0 & class_a == 0)

#Calculate count, median rent, median leasing rate for green buildings
greenCount <- greenOnly %>% summarise(n())
medGreenCapacity <- greenOnly %>% summarise(median(leasing_rate)/100)
medGreenRent <- greenOnly %>%   summarise(median(Rent))


#Calculate count, median rent, median leasing rate for non-green buildings
nonGreenCount <- nonGreen %>% summarise(n())
medNonGreenCapacity <- nonGreen %>% summarise(median(leasing_rate)/100)
medNonGreenRent <- nonGreen %>% summarise(median(Rent))

#Calculate median gas and electric cost 
medGasCost <- gb %>% summarise(median(Gas_Costs))
medElectricCost <- gb %>% summarise(median(Electricity_Costs))

#setSquareFootage for further calculations
sqFt = 250000
#Set a weight of .9 for green electric and gas cost since they use less than non-green buildings. 
#This is a subjective number and can be changed with future research regarding how much will actually be saved
greenCostWeighted = .9

#Calculate expected rent, expense, and profit if our building was green
#Weight rent by expected capacity and calculate rent by adding rent diff b/w green/non green buildings
#and adding that to the median non green rent. 
greenExpectedRent <- medGreenRent * medGreenCapacity * sqFt
#Weight expenses by expected savings by using less resources
greenExpectedExpense <- (sqFt * medGasCost * greenCostWeighted) + (sqFt * medElectricCost * greenCostWeighted)
greenExpectedProfit <- greenExpectedRent - greenExpectedExpense

#Calculate expected rent, expense, and profit if our building was not green. 
#Weight rent by expected capacity and calculate rent by multiplying square feet by median rent of non green
#buildings. Expected expenses was not weighted because they will use all resources.

nonGreenExpectedRent <- medNonGreenRent * medNonGreenCapacity * sqFt
nonGreenExpectedExpense <- (sqFt * medGasCost) + (sqFt * medElectricCost)
nonGreenExpectedProfit <- nonGreenExpectedRent - nonGreenExpectedExpense

#Calculate the expected profit difference if the building chose to be green
buildingDiff <- greenExpectedProfit-nonGreenExpectedProfit


#Set green premium so we can calculate expected payback period and long-haul profits
options("scipen" = 100,"digits" = 4) #Gets rid of scientific notation
greenCert <- 100000000 *.05

paybackPeriod = greenCert/buildingDiff

print("Report")
paste0("Expected rent price for Green building: ",medGreenRent, " Expected rent price for Non-Green building:",medNonGreenRent )
paste0("Expected leasing rate for Green building: ",medGreenCapacity, " Expected rent price for Non-Green building:",medNonGreenCapacity )
paste0("Expected yearly rent for Green building: ",round(greenExpectedRent,2), " Expected yearly rent for Non-Green building:", round(nonGreenExpectedRent,2))
paste0("Expected electric Rate for the building: ",medElectricCost, " Expected gas Rate for the building: ",medGasCost )
paste0("Expected electric/gas usage for the Green building: ",greenCostWeighted, " Expected electric/gas usage for the Non-Green Building: 1" )
paste0("Expected expenses for the Green building: ",round(greenExpectedExpense,2), " Expected expenses for the Non-Green building: ",round(nonGreenExpectedExpense,2 ))
paste0("Expected profit for Green Building: ",round(greenExpectedProfit,2), " Expected profit for Non-Green Building: ",round(nonGreenExpectedProfit,2) )
paste0("Expected profit difference between a green and non-green building: ", round(buildingDiff,2))
paste0("Expected payback period: ", round(paybackPeriod,2))
```

In conclusion, we suggest that the Austin real-estate developer should only compete in the non class a market if they decided to make a green building. That is because a non class a green building will generate more profit resulting in a shorter pay back period. 
# office hour note: can use logistic regression on y (green_Rating) and x (class_a) to see if x has a significant impact on y. 