---
title: "R_HW_4_Market Segmentation"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
tweets <- read.csv("social_marketing.csv")
tweets <- tweets[,-1]
tweets <- tweets %>% filter(spam != 1 & adult != 1)
```

## First, let's take a look at data correlation.
Practically, if our data is not highly correlated, we might not need a PCA.
As the graph shows, some of our variables are quite correlated.Thus, we can proceed to PCA and create a smaller subset of variables.

```{r}
# Creating a correlation plot
library(ggcorrplot)
cormat <- round(cor(tweets), 2)
ggcorrplot::ggcorrplot(cor(cormat), hc.order = TRUE)
```


```{r}
# PCA
pr_out <-prcomp(tweets, center = TRUE, scale = TRUE) #Scaling data
summary(pr_out)
```

```{r}
# The first principal component accounts for 12.47% of the data variance.
# This is the highest proportion
pr_var <-  pr_out$sdev ^ 2
pve <- pr_var / sum(pr_var)
plot(pve, xlab = "Principal Component", ylab = "Proportion of Variance Explained", ylim = c(0,1), type = 'b')
```


```{r}
# Cumulative PVE plot
plot(cumsum(pve), xlab = "Principal Component", ylab = "Cumulative Proportion of Variance Explained", ylim =c(0,1), type = 'b')
```


```{r}
varimax(pr_out$rotation[, 1:10])
```

```{r}
library(tidyverse)
library(FactoMineR)
library(factoextra)

tweets_scale <- scale(tweets)
pca_tweets <- PCA(tweets_scale, 
                scale.unit = FALSE,
                graph = F, 
                ncp = 10) #default: 5)
summary(pca_tweets)
```

```{r}
plot.PCA(pca_tweets, 
         choix = c("ind"),
         habillage = 1,
         select = "contrib5",
         invisible = "quali")
```

```{r}
plot.PCA(pca_tweets, choix = c("var"))
```

```{r}
pca_dimdesc <- dimdesc(pca_tweets)
pca_dimdesc$Dim.1
```

```{r}
tweets_new <- tweets[-c(2260,2389,3227,3998,7059),] #get rid of outliers
tweets_scale1 <- scale(tweets_new)
```

```{r}
RNGkind(sample.kind = "Rounding") #to get the set.seed numbers not changed everytime executed
kmeansTunning <- function(data, maxK) {
  withinall <- NULL
  total_k <- NULL
  for (i in 1:maxK) {
    set.seed(101)
    temp <- kmeans(data,i)$tot.withinss
    withinall <- append(withinall, temp)
    total_k <- append(total_k,i)
  }
  plot(x = total_k, y = withinall, type = "o", xlab = "Number of Cluster", ylab = "Total within")
}

# kmeansTunning(your_data, maxK = 5)
kmeansTunning(tweets_scale1, maxK = 20)
```

## From above figure, we can choose 6 or 10 clusters.

## Let's see if we set centers equal to 6.

```{r}
RNGkind(sample.kind = "Rounding") 
#to get the set.seed numbers not changed everytime executed

set.seed(101)
tweets_cluster1 <- kmeans(tweets_scale1, centers = 6)

fviz_cluster(tweets_cluster1, data = tweets_scale1)
```

```{r}
tweets_new$cluster1 <- tweets_cluster1$cluster
tweets_new
```

## The biggest cluster is cluster #3, which account for 51% out of 6 six clusters.

```{r}
round(prop.table(table(tweets_new$cluster1)),2)
library(dplyr)
tweets_new %>% 
  group_by(cluster1) %>% 
  summarise(count=n())
```
## Clusters Profiling
The characteristic summary of NutrientH20's Twitter followers in the same cluster are as follows:

Cluster 1: Highest sports_fandom, food, family, crafts, religion, parenting, school
Cluster 2: Highest travel, politics, news, computers, automotive
Cluster 3: Nothing special?
Cluster 4: Highest online_gaming, college_uni, sports_playing, art, spam
Cluster 5: Highest health_nutrition, eco, outdoors, personal_fitness
Cluster 6: Highest chatter, current_events, photo_sharing, uncategorized, tv_film, home_and_garden, music, shopping, cooking, business, beauty, dating, fashion, small_business, adult

```{r}
library(dplyr)
prof1=tweets_new %>% 
      group_by(cluster1) %>% 
      summarise_all('mean')
prof1
t(data.frame(prof1,row.names=1))
```

```{r}
library(dplyr)
a=data.frame(tweets_scale1)
a$cluster1 <- tweets_cluster1$cluster
prof3=a %>% 
      group_by(cluster1) %>% 
      summarise_all('mean')
prof3
t(data.frame(prof3,row.names=1))
```


## Let's see if we set centers equal to 10.

```{r}
RNGkind(sample.kind = "Rounding") 
#to get the set.seed numbers not changed everytime executed

set.seed(101)
tweets_cluster2 <- kmeans(tweets_scale1, centers = 10)

fviz_cluster(tweets_cluster2, data = tweets_scale1)
```

```{r}
tweets_new$cluster2 <- tweets_cluster2$cluster
tweets_new
```
## The biggest cluster is cluster #9, which account for 43% out of 10 six clusters.

```{r}
round(prop.table(table(tweets_new$cluster2)),2)
library(dplyr)
tweets_new %>% 
  group_by(cluster2) %>% 
  summarise(count=n())
```
## Clusters Profiling

```{r}
library(dplyr)
prof2=tweets_new %>% 
      group_by(cluster2) %>% 
      summarise_all('mean')
prof2
t(data.frame(prof2,row.names=1))
```

```{r}

```


