---
title: "R_HW_3_Portfolio Modeling"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages('mosaic')
#install.packages('quantmod')
#install.packages('foreach')
#install.packages("getSymbols")
```

## Portfolio (1) —— Aggressive Portfolio

Currency ETFs (20%) + Corporate Bonds ETFs (30%) + Equities ETFs (50%)

```{r}
library(mosaic)
library(quantmod)
library(foreach)

mystocks = c("UUP", "FXE", "VCIT", "LQD", "FXI", "EWJ")
myprices = getSymbols(mystocks, from = "2010-01-01")

# A chunk of code for adjusting all stocks
# creates a new object adding 'a' to the end
for(ticker in mystocks) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}

# Combine all the returns in a matrix
all_returns = cbind(ClCl(UUPa),
								ClCl(FXEa),
								ClCl(VCITa),
								ClCl(LQDa),
								ClCl(FXIa),
								ClCl(EWJa))
head(all_returns)
all_returns = as.matrix(na.omit(all_returns))


library(foreach)
# Now simulate many different possible futures
# just repeating the above block thousands of times
initial_wealth = 100000

set.seed(1) #make sure we use same return every time running this model

sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	weights = c(0.1,0.1,0.15,0.15,0.25,0.25) #aggressive portfolio
	holdings = weights * total_wealth
	n_days = 20
	wealthtracker = rep(0, n_days)
	for(today in 1:n_days) {
	  # Sample a random return from the empirical joint distribution
    # This simulates a random day
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		wealthtracker[today] = total_wealth
		weights = c(0.1,0.1,0.15,0.15,0.25,0.25) #portfolios are rebalanced each day
		holdings = weights * total_wealth #portfolios are rebalanced each day
	}
	wealthtracker
}

# each row is a simulated trajectory
# each column is a data
head(sim1)

hist(sim1[,n_days], 25)

# Profit/loss
mean(sim1[,n_days])
mean(sim1[,n_days] - initial_wealth)
hist(sim1[,n_days]- initial_wealth, breaks=30)

# 5% value at risk:
quantile(sim1[,n_days]- initial_wealth, prob=0.05)

# note: this is  a negative number (a loss, e.g. -500), but we conventionally
# express VaR as a positive number (e.g. 500)

# 95% value at risk:
quantile(sim1[,n_days]- initial_wealth, prob=0.95)

#Return per day graph over the total time
day_profit = c()
for (i in 1:n_days){
  day_profit[i] = mean(sim1[,i])
}
num_days=1:n_days
return_df=data.frame(day_profit,num_days)
max(return_df)
ggplot(data=return_df) + geom_line(mapping=aes(x=num_days,y=day_profit)) +
  ggtitle("Aggressive Portfolio Returns ") + xlab("Days") + ylab("Return ($)")
```

## Portfolio (2) —— Moderate Portfolio

Currency ETFs (30%) + Corporate Bonds ETFs (50%) + Equities ETFs (20%)

```{r}
library(mosaic)
library(quantmod)
library(foreach)

mystocks = c("UUP", "FXE", "VCIT", "LQD", "FXI", "EWJ")
myprices = getSymbols(mystocks, from = "2010-01-01")

# A chunk of code for adjusting all stocks
# creates a new object adding 'a' to the end
for(ticker in mystocks) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}

# Combine all the returns in a matrix
all_returns = cbind(ClCl(UUPa),
								ClCl(FXEa),
								ClCl(VCITa),
								ClCl(LQDa),
								ClCl(FXIa),
								ClCl(EWJa))
head(all_returns)
all_returns = as.matrix(na.omit(all_returns))


library(foreach)
# Now simulate many different possible futures
# just repeating the above block thousands of times
initial_wealth = 100000

set.seed(1) #make sure we use same return every time running this model

sim2 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	weights = c(0.15,0.15,0.25,0.25,0.1,0.1) #moderate portfolio
	holdings = weights * total_wealth
	n_days = 20
	wealthtracker = rep(0, n_days)
	for(today in 1:n_days) {
	  # Sample a random return from the empirical joint distribution
    # This simulates a random day
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		wealthtracker[today] = total_wealth
		weights = c(0.15,0.15,0.25,0.25,0.1,0.1) #portfolios are rebalanced each day
		holdings = weights * total_wealth #portfolios are rebalanced each day
	}
	wealthtracker
}

# each row is a simulated trajectory
# each column is a data
head(sim2)
hist(sim2[,n_days], 25)

# Profit/loss
mean(sim2[,n_days])
mean(sim2[,n_days] - initial_wealth)
hist(sim2[,n_days]- initial_wealth, breaks=30)

# 5% value at risk:
quantile(sim2[,n_days]- initial_wealth, prob=0.05)

# note: this is  a negative number (a loss, e.g. -500), but we conventionally
# express VaR as a positive number (e.g. 500)

# 95% value at risk:

quantile(sim2[,n_days]- initial_wealth, prob=0.95)

quantile(sim2[,n_days]- initial_wealth, prob=0.95)

#Return per day graph over the total time
day_profit = c()
for (i in 1:n_days){
  day_profit[i] = mean(sim2[,i])
}
num_days=1:n_days
return_df=data.frame(day_profit,num_days)
max(return_df)
ggplot(data=return_df) + geom_line(mapping=aes(x=num_days,y=day_profit)) +
  ggtitle("Moderate Portfolio Returns ") + xlab("Days") + ylab("Return ($)")

```

## Portfolio (3) —— Conservative Portfolio

Currency ETFs (50%) + Corporate Bonds ETFs (30%) + Equities ETFs (20%)

```{r}
library(mosaic)
library(quantmod)
library(foreach)

mystocks = c("UUP", "FXE", "VCIT", "LQD", "FXI", "EWJ")
myprices = getSymbols(mystocks, from = "2010-01-01")

# A chunk of code for adjusting all stocks
# creates a new object adding 'a' to the end
for(ticker in mystocks) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}

# Combine all the returns in a matrix
all_returns = cbind(ClCl(UUPa),
								ClCl(FXEa),
								ClCl(VCITa),
								ClCl(LQDa),
								ClCl(FXIa),
								ClCl(EWJa))
head(all_returns)
all_returns = as.matrix(na.omit(all_returns))


library(foreach)
# Now simulate many different possible futures
# just repeating the above block thousands of times
initial_wealth = 100000

set.seed(1) #make sure we use same return every time running this model

sim3 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	weights = c(0.25,0.25,0.15,0.15,0.1,0.1) #conservative portfolio
	holdings = weights * total_wealth
	n_days = 20
	wealthtracker = rep(0, n_days)
	for(today in 1:n_days) {
	  # Sample a random return from the empirical joint distribution
    # This simulates a random day
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		wealthtracker[today] = total_wealth
		weights = c(0.25,0.25,0.15,0.15,0.1,0.1) #portfolios are rebalanced each day
		holdings = weights * total_wealth #portfolios are rebalanced each day
	}
	wealthtracker
}

# each row is a simulated trajectory
# each column is a data
head(sim3)
hist(sim3[,n_days], 25)

# Profit/loss
mean(sim3[,n_days])
mean(sim3[,n_days] - initial_wealth)
hist(sim3[,n_days]- initial_wealth, breaks=30)

# 5% value at risk:
quantile(sim3[,n_days]- initial_wealth, prob=0.05)

# note: this is  a negative number (a loss, e.g. -500), but we conventionally
# express VaR as a positive number (e.g. 500)

# 95% value at risk:

quantile(sim3[,n_days]- initial_wealth, prob=0.95)

#Return per day graph over the total time
day_profit = c()
for (i in 1:n_days){
  day_profit[i] = mean(sim3[,i])
}
num_days=1:n_days
return_df=data.frame(day_profit,num_days)
max(return_df)
ggplot(data=return_df) + geom_line(mapping=aes(x=num_days,y=day_profit)) +
  ggtitle("Safe Portfolio Returns ") + xlab("Days") + ylab("Return ($)")

```

Across the three portfolios, we can see that the return on average increases over the 20 days period. However, the aggressive model return vs days line graph fluctuate a little bit more then the other two portfolios. This can be seen on the VaR as well, while the aggressive portfolio has the highest average return, it also has the highest VaR at 5%. Comparing the returns and VaR of all three models, the moderate portfolio is the best option for us because it has a relatively high return that not too far from that of the agreesive model(100296.8 vs 100325.4) and a 5% VaR that is far lower then the of the aggressive model(2060.641 vs 4354.693). The conservative model on the other hand have the lowerst VaR (1870.43) but the return (100203.6) is also the lowest therefore we don't think it is the best option comparing to the moderate model. 