---
title: "R_HW_1_Greenhouse"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages('ggplot2')
```

```{r}
buildings <- read.csv("greenbuildings.csv")

library(dplyr)

green = dplyr::filter(buildings,green_rating==1)
nongreen = dplyr::filter(buildings,green_rating==0)
```

Let's take a look at how the rents and occupancy rates of green buildings and non-green buildings are distributed.

```{r}
library(ggplot2)
theme_set(theme_classic())

g1 <- ggplot(buildings, aes(Rent)) + scale_fill_brewer(palette = "Spectral") +                geom_histogram(aes(fill=stories),binwidth = 2, 
                   col="black", 
                   size=.1)

g1 + facet_wrap( ~ green_rating) + 
    labs(title="Distribution of rent across all buildings", y="Number of buildings", x="Rent")

# Zoom in without deleting the points outside the limits.
g1 + facet_wrap( ~ green_rating) + coord_cartesian(xlim=c(0,100)) +
    labs(title="Distribution of rent across all buildings", subtitle="Rent below $100",
    y="Number of buildings", x="Rent")

# Zoom in to take a look at the extreme case.
g1 + facet_wrap( ~ green_rating) + coord_cartesian(xlim=c(100,300),ylim=c(0,25)) +
  labs(title="Distribution of rent across all buildings", subtitle="Rent above $100",
    y="Number of buildings", x="Rent")
```

```{r}
g2 <- ggplot(buildings, aes(leasing_rate)) + scale_fill_brewer(palette = "Spectral") +                geom_density(aes(fill=factor(green_rating)), alpha=0.8)
g2 + facet_wrap( ~ green_rating) + 
    labs(title="Distribution of leasing rate across all buildings", y="Density", x="Leasing Rate")
```

There are many factors that can have an effect on rent, like location, building quality, appliances and Other amenities, tenant/use mix, etc. Now we know that the target project is a new 15-story mixed-use building on East Cesar Chavez, just across I-35 from downtown. Since we have story information in the dataset, let's focus on the situation of 15-story buildings.

From the graphic, we can conclude that among 15-story building:
1.the average rent of green buildings is higher than that of non-green buildings;
2.the average occupancy rate of green buildings is higher than that of non-green buildings;
3.all green buildings have a class of a or b (however, does this bring extra cost)?

```{r}
library(dplyr)

story15 = dplyr::filter(buildings,stories==15)
story15.class = story15 %>% filter(class_a == 0 & class_b == 0)

library(ggplot2)
library(ggalt)
theme_set(theme_bw())
g3 <- ggplot(story15, aes(leasing_rate,Rent))
g3 + geom_point(aes(col=green_rating, size=age)) + 
     geom_encircle(aes(x=leasing_rate, y=Rent), 
                data=story15.class, 
                color="red", 
                size=2, 
                expand=0.08)
```

